General purpose gene annotation using deep learning

### 2020-04-16 paper/main.tex
trees
updated results with test plant genomes

\begin{table}[!t]
\processtable{Experimental Results and Comparison\label{tab:results}} {
\begin{tabular}{@{}lll@{}}
\toprule & Animals & Plants\\
\midrule
AUGUSTUS & 0.632 (+-0.089) & 0.749 (+-0.161)\\
Dilated CNN Baseline & - (+-) & - (+-)\\
Best Helixer model & - (+-) & - (+-) \\
Best model + varied input length & - (+-) & - \\
Best model (+ varied input length) + overlapping &  0.85 (+-0.068) & 0.843 (+-0.151) \\
(Varied input length +) overlapping + ensembling & 0.868 (+-0.064) & 0.863 (+-0.148) \\
\botrule
\end{tabular}}{Values are the median in Subgenic F1 across all validation and test genomes of the respective group. Varied input length was only used in the animal case. The best model was chosen out of the eight models of the ensemble for having the best performance in the reported setup. The AUGUSTUS result is the median score for all genomes.}
\end{table}

>>>>

\begin{table}[!t]
\processtable{Experimental Results and Comparison\label{tab:results}} {
\begin{tabular}{@{}lll@{}}
\toprule & Animals & Plants\\
\midrule
AUGUSTUS & 0.632 (+-0.089) & 0.747 (+-0.188)\\
Dilated CNN Baseline & - (+-) & - (+-)\\
Best Helixer model & - (+-) & - (+-) \\
Best model + varied input length & - (+-) & - \\
Best model (+ varied input length) + overlapping &  0.85 (+-0.068) & 0.843 (+-0.151) \\
(Varied input length +) overlapping + ensembling & 0.868 (+-0.064) & 0.863 (+-0.148) \\
\botrule
\end{tabular}}{Values are the median in Subgenic F1 across all validation and test genomes of the respective group. Varied input length was only used in the animal case. The best model was chosen out of the eight models of the ensemble for having the best performance in the reported setup. The AUGUSTUS result is the median score for all genomes.}
\end{table}
